Project Uccle

### 2020-06-06 project.mems.Rmd
add - in file pattern

```{r set mems, include=FALSE}
# MEMS
domain <- c(-7200,7200); pattern <- "MEM.*\\.csv"; name <- "MEM"; description <- "Membach"; proj_file <- 'proj.mems.RData'
```

>>>>

```{r set mems, include=FALSE}
# MEMS
domain <- c(-7200,7200); pattern <- "MEMS-.*\\.csv"; name <- "MEM"; description <- "Membach"; proj_file <- 'proj.mems.RData'
```

### 2020-06-06 project.uccs.Rmd
delivered draft
add - in file pattern

```{r set uccs, include=FALSE}
# UCCS
domain <- c(-350000,350000); pattern <- "UCCS.*\\.csv"; name <- "UCCS"; description <- "Uccle, Bruxelles"; proj_file <- 'proj.uccs.RData'
```

@@

>>>>

```{r set uccs, include=FALSE}
# UCCS
domain <- c(-350000,350000); pattern <- "UCCS-.*\\.csv"; name <- "UCCS"; description <- "Uccle, Bruxelles"; proj_file <- 'proj.uccs.RData'
```

@@

```{r final model selection}
chosen.model <- c(2,0,0,0,1,1)
chosen.lambda <- NULL
```

```{r project.after, child='project.after.Rmd'}
```
